\documentclass[11pt, letterpaper]{article}

% Import Packages:
\usepackage[
    top=10mm, % seperation between body and page edge from the top,
    ignoreheadfoot, % set margins without considering header and footer
    bottom=5 mm, % seperation between body and page edge from the bottom
    left=9mm, % seperation between body and page edge from the left
    right=9mm, % seperation between body and page edge from the right
    % footskip=1.0 cm, % seperation between body and footer
    % showframe % for debugging 
]{geometry} % for adjusting page geometry
\usepackage{titlesec} % for customizing section titles
\usepackage{tabularx} % for making tables with fixed width columns
\usepackage{array} % tabularx requires this
\usepackage[usenames,dvipsnames]{color} %using the color package, not xcolor
\definecolor{customGreen}{rgb}{0.84, 0.9, 0.8}
\definecolor{linecolor}{rgb}{0.54, 0.65, 0.6}
\definecolor{customPink}{rgb}{.96, 0.91, 0.92}
\definecolor{primaryColor}{rgb}{0, 0, 0}
\usepackage{enumitem} % for customizing lists
\usepackage[
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref} % for links, metadata and bookmarks
\usepackage[pscoord]{eso-pic} % for floating text on the page
\usepackage{calc} % for calculating lengths
\usepackage{bookmark} % for bookmarks
\usepackage{lastpage} % for getting the total number of pages
\usepackage{changepage} % for one column entries (adjustwidth environment)
\usepackage{paracol} % for two and three column entries
\usepackage{ifthen} % for conditional statements
\usepackage{needspace} % for avoiding page brake right after the section title
\usepackage{iftex} % check if engine is pdflatex, xetex or luatex

% Ensure that generate pdf is machine readable/ATS parsable:
\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[T1]{fontenc}
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi

\usepackage{charter}

% Some settings:
\raggedright
\setlength{\columnsep}{0.5cm} % set column seperation
\pagenumbering{gobble} % no page numbering

\titleformat{\section}{\needspace{2\baselineskip}\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule]

\titlespacing{\section}{
    % left space:
    -1pt
}{
    % top space:
    .2 cm
}{
    % bottom space:
    0.1 cm
} % section title spacing

% Redefine new section with colorbox
\newcommand{\mysectionheading}[1]{
  \setlength{\fboxsep}{2pt}
  \colorbox{customPink}{\textbf{\large\uppercase{#1}}}
  \vspace{-.7em}
  \par\noindent\textcolor{linecolor}{\rule{\linewidth}{0.6 mm}}
  \vspace{-1.25em}
}

% Create education heading. Parameters: deg, loc, date, gpa
\newcommand{\educationHeading}[4]{
\runsubsection{#1}
\hspace*{\fill}
Graduation Date: \location{\textbf{#3}}
\\
\descript{#2}
\hspace*{\fill}
GPA:\textbf{#4}\\

}
% Create Study Abroad heading. Parameters: name, loc, date, description1, description2
\newcommand{\studyAbroad}[4]{
\runsubsection{#1}
\hspace*{\fill}
\location{\textbf{#3}}
\\
\textit{\descript{#2}}
\\
\descript{#4}
}

% Create High School heading. Parameters: name, date, description
\newcommand{\highschool}[3]{
\runsubsection{#1}
\hspace*{\fill}
\location{\textbf{#2}}
\\
\descript{#3}
}
% Parameters: courses
\newcommand{\listing}[2]{
    \vspace{-0.9em}
\par\noindent\textcolor{linecolor}{\rule{\linewidth}{0.2 mm}}
\vspace{-1.25em}
    \textbf{#1}
    \descript{#2}
}
% Bullet Lists with fewer gaps command
\newenvironment{bullets}{
\vspace{-1.8mm}
\normalsize
\fontsize{10pt}{10pt}
\vspace{-1.5mm}
\begin{itemize}[leftmargin=*]
\itemsep1pt 
\parskip1.5pt 
\parsep1.5pt
}{
\end{itemize}
\vspace{-1.8mm}
}
% headings command - create different types of heading
\newcommand{\runsubsection}[1]{%
\color{primaryColor}%
% \customLatoBlack%
\fontsize{12pt}{12pt}%
\selectfont%
\bfseries%
#1%
\normalfont}%

\newcommand{\courseWork}[1]{\textbf{Relevant Coursework:} #1}

\newcommand{\skills}[1]{
    \vspace{-.7em}
  \par\noindent\textcolor{linecolor}{\rule{\linewidth}{0.6 mm}}
  \vspace{-1.25em}\textbf{Skills:} #1}

\newcommand{\tools}[1]{\textbf{Tools:} #1}

% Descriptors command
\newcommand{\descript}[1]{%
\color{primaryColor}%
\raggedright%
% \scshape%
% \customLatoRegular%
\fontsize{11pt}{13pt}%
\selectfont{#1}%
\normalfont}

% Location command
\newcommand{\location}[1]{%
\color{primaryColor}%
\raggedright%
% \customLatoBlack%
\fontsize{11pt}{13pt}%
\selectfont{#1}%
\normalfont}


% Minor command -  even smaller sub section
\newcommand{\minorSection}[1]{%
\color{primaryColor}%
\raggedright%
\scshape%
% \customRalewayMedium%
\fontsize{11pt}{12pt}%
% \selectfont{#1}%
\normalfont}

% Simulate new line
\newcommand{\fakeNewLine}{\newline \vspace{-\baselineskip}}

% Header
\newenvironment{header}{
    \setlength{\topsep}{0pt}\par\kern\topsep\centering\linespread{1.5}
}{
    \par\kern\topsep
} 

% Roles heading. Parameters: Company, role, date
\newcommand{\sectionHeadingSmall}[3]{\runsubsection{\uppercase{#1}}\descript{ |
#2}\hfill\textbf{\location{\hspace*{4pt} #3}}\vspace{-0.9em}
\par\noindent\textcolor{linecolor}{\rule{\linewidth}{0.2 mm}}
\vspace{-1.25em}} 

% Projects heading. Parameters: name, date
\newcommand{\projHeadingSmall}[2]{\runsubsection{\uppercase{#1}}\hfill\textbf{\location{\hspace*{4pt} #2}}\vspace{-.7em}
\par\noindent\textcolor{linecolor}{\rule{\linewidth}{0.2 mm}}
\vspace{-1.25em}} 

\begin{document}
% vertical lines


\newcommand{\sectionsep}[0]{\vspace{4pt}}

%--------------------------------------------------------------
%     Profile
%--------------------------------------------------------------
    \newcommand{\AND}{\unskip
        \cleaders\copy\ANDbox\hskip\wd\ANDbox
        \ignorespaces
    }
    \newsavebox\ANDbox
    \sbox\ANDbox{$|$}

% header section
    \begin{header}
        \fontsize{25 pt}{15 pt}\selectfont Vanessa Isabel Roque
        \vspace{0.3 pt}
        \normalsize

        \mbox{\href{mailto:viroque19@gmail.com}{viroque19@gmail.com}}%
        \kern 5.0 pt\AND\kern 5.0 pt%
        \mbox{\href{tel:+1-330-730-9139}{330 730 9139}}%
        \kern 5.0 pt\AND\kern 5.0 pt%
        \mbox{\href{https://linkedin.com/in/vanessairoque/}{linkedin.com/in/vanessairoque}}%
        \kern 5.0 pt\AND\kern 5.0 pt%
        \mbox{\href{https://github.com/vroque19}{github.com/vroque19}}%
    \end{header}

    \vspace{5 pt-0.2 cm}

\sectionsep

% education section
\mysectionheading{education}

\educationHeading{California State University, Fullerton}{B.S/M.S Computer Engineering, Computer Science Minor}{May 2025}{3.6}

\vspace{1mm}
\studyAbroad{Korea University | Seoul, South Korea}{Study Abroad Reciprocal Exchange Program}{Fall 2023}{Attended one of South Korea’s most prestigious universities to cultivate a global perspective through an immersive cultural experience.}

\vspace{1mm}
\courseWork{Data Structures, Algorithms, Object-Oriented Programming, Databases, Operating Systems, Computer Networks, Embedded Systems, Computer Architecture, Real-Time Audio Processing, Signals and Systems, Electronic Circuits, Linear Algebra and Differential Equations, Multivariate Calculus}

% \vspace{1mm}

\sectionsep
\mysectionheading{experience}

\sectionHeadingSmall{California State University, Fullerton}{Supplemental Instructor}{January 2023 - Present}
\begin{bullets}
    \item Explain complex Calculus III concepts to students by hosting collaborative learning sessions twice a week.
    \item Thoughtfully organize each session by preparing relevant study materials, boosting students' grades by 10\%.
\end{bullets}

\sectionHeadingSmall{Rosendin Elecrtic Co.}{Electrical Engineering Intern}{June 2024 - August 2024}
\begin{bullets}
    \item Developed electrical designs and specifications for power, lighting, and control systems in Autodesk Revit.
    \item Used Visual Lighting to create comprehensive lighting designs for commercial buildings and perform photometric analysis to ensure standards for brightness, intensity and energy efficiency are met.
    \item Conducted QA QC in Bluebeam to identify potential issues in schedules, single line diagrams, and drawings.

    \item Attended site visits to inspect the installation of electrical components such as conduits, transformers, and fixtures.
\end{bullets}

\sectionHeadingSmall{Summer undergraduate research academy}{Researcher}{June 2024 - August 2024}
\begin{bullets}
    \item Investigated various wireless power transfer technologies and identified magnetic resonance as an improvement to current inductive technologies and a potential future trend for electric vehicles.
    \item Built and tested a small-scale LLC resonant converter, collaborating with my research partner. We identified optimal tuning to improve charging efficiency and minimize interference from other devices.
    \item Presented our work at the SUReA conference at California State University, Fullerton.
\end{bullets}

\mysectionheading{Projects}

\projHeadingSmall{Smart Sleep Hub}{Fall 2024 - Present}\begin{bullets}

    \item Designed and developed a device that promotes a healthy sleep environment by regulating light exposure and recording sleep data via light, motion, and temperature sensors.
    \item Interfaced a Raspberry Pi 5 with a touchcscreen to display a clock, enable sleep configuration, and view their sleep data. Developed the UI using SvelteKit, Javascript, TailwindCSS, and Vite.
    \item  Integrated Philips Hue RESTful API that allows the hub to control bedroom light color and intensity.
    \item Conducting tests in a team to ensure seamless integration of software and hardware.
\end{bullets}

\projHeadingSmall{Recipe Keeper iOS App}{Fall 2024 - Present}

\begin{bullets}
    \item Developed an IOS app to simplify recipe management so creating, updating and viewing recipes can be effortless.

    \item Designed a user-friendly interface using SwiftUI to enhance user experience and ensure seamless navigation.
    % \item Implemented a feature to parse URL data, automatically generating recipes from online sources using web scraping and natural language processing.
\end{bullets}

\mysectionheading{Extracurriculars}

\sectionHeadingSmall{Association for Computing Machinery}{Board Member}{2022 - present}
\begin{bullets}
    \item Gain a deeper understanding of computer science through hands-on programming workshops and events.
\end{bullets}
\sectionHeadingSmall{Engineering Design Club}{Member}{2022 - present}
\begin{bullets}
    \item Circuit and program Adafruit Feather RP2040 RFM69 in CircuitPython for 3D printed Pokeball last semester
    \item Gain experience in soldering, 3D printing, solidworks, and PCB by attending hands-on workshops.
\end{bullets}
 
% skills and tools

\skills{Python, C/C++, HTML, Javascript, TailwindCSS, MySQL, SwiftUI, SvelteKit}
\vspace{5mm}

\tools{VS Code, Git, GitHub, XCode, Code Composer Studio}

\end{document}
